Type-Safe Modular Parsing

### 2016-11-29 paper/paper.tex
Typos

  Over the years alot of effort has been put on solving challenging
  extensibility problems, while retaining important software
  engineering properties such as modular type-safety and
  separate compilation. Most previous work focused on
  operations that traverse and process extensible Abtract Syntax Tree
  (AST) structures. However, there is almost no work on operations that
  \emph{build} such extensible ASTs, including \emph{parsing}.

>>>>

  Over the years a lot of effort has been put on solving challenging
  extensibility problems, while retaining important software
  engineering properties such as modular type-safety and
  separate compilation. Most previous work focused on
  operations that traverse and process extensible Abstract Syntax Tree
  (AST) structures. However, there is almost no work on operations that
  \emph{build} such extensible ASTs, including \emph{parsing}.
